\documentclass[a4paper,11pt]{article}

\usepackage[a4paper, total={6in, 9in}]{geometry}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	urlcolor=black
}

\begin{document}
	\title{ C Programming Course Syllabus }
		\author{ Prepared by \em{Shakil Shahadat} }
		\date{ 2021 }
	\maketitle

	\thispagestyle{empty} % No page number in the first page

	\vspace*{\fill} % Print the following line at the end of the page
	\noindent “One must learn by doing the thing; for though you think you know it, you have no certainty, until you try.” - Sophocles


	\newpage

\em
	\section*{ Chapter 1: Introduction to C Programming }
	\begin{enumerate}
		\item What is Programming \& Programming Languages?
		\item History of Programming
		\item Categories of Programming Languages
		\item Major Programming Languages
		\item What can be done with Programming?
		\item History of C Programming Language
		\item Why C?
		\item Difference between C \& C++
		\item Introduction to C Programming Language
		\item Prerequisites for Learning C
		\item How to Write a Program: Text Editor vs Code Editor vs IDE
		\item Download and Install \href{https://www.codeblocks.org/}{ Code::Blocks }
		\item How to Run a C Program?
		\item What is a Compiler?
		\item Running ‘Hello World’ program: Extension, Code, Execution
		\item Suggested Books \& Resources
	\end{enumerate}


	\newpage

	\section*{ Chapter 2: Variable, Data Types, Constant, Comment }

	\begin{enumerate}
		\item Basic Structure of a C Program
		\item Statement \& Closing Semi-colon
		\item What is Variable?
		\item Variable Declaration
		\item Data Types
		\item Naming Convention, Do’s \& Don't
		\item Reserved Words
		\item Case Sensitivity
		\item Variable Assignment
		\item Single \& Double Quotes
		\item Constant
		\item Code Readability
		\item Code Formatting
		\item Comment
	\end{enumerate}


	\section*{ Chapter 3: Function }

	\begin{enumerate}
		\item DRY Principle
		\item Code Block
		\item Philosophy of Function
		\item Function Declaration
		\item Naming Convention, Case Sensitivity, Do’s \& Don't
		\item Function Execution
		\item Function Argument
		\item Default Value of an Argument
		\item Passing Arguments by Reference
		\item Function with a Return Value
		\item Variable Scope: Local and Global Variable
		\item Recursion
		\item Usage of Functions
	\end{enumerate}


	\section*{ Chapter 4: Operators \& Expression }

	\begin{enumerate}
		\item Definition of Operator \& Operand
		\item Types of Operators
		\item Expression
		\item Arithmetic Operators
		\item Assignment Operators
		\item Increment / Decrement Operators
		\item Comparison Operators
		\item Logical Operators
		\item Hierarchy of Operators
		\item Associativity of Operators
	\end{enumerate}


	\section*{ Chapter 5: Conditional Statements }

	\begin{enumerate}
		\item If Statement
		\item Else Statement
		\item Else-If Statement
		\item Nested Statement
		\item Switch Statement
		\item Break Statement
		\item Comma Operator
		\item Goto Statement
	\end{enumerate}


	\section*{ Chapter 6: Loop Statement }

	\begin{enumerate}
		\item What are Loop Statements?
		\item Types of Loop Statements
		\item For Loop
		\item Infinite Loop
		\item Special Cases of For Loop
		\item While Loop
		\item Do/While Loop
		\item Continue Statement
		\item Writing Repetitive Code: Comparison between Function \& Loop
	\end{enumerate}


	\section*{ Chapter 7: Array }

	\begin{enumerate}
		\item What is an Array?
		\item Indexed Array
		\item Associative Array
		\item Multi-dimensional Array
	\end{enumerate}


	\section*{ Chapter 8: Pointers }

	\begin{enumerate}
		\item What is Pointer?
		\item Declaration of Pointers
		\item Passing Pointers to Functions
		\item Operations on Pointers
		\item Arrays of Pointers
		\item Passing Functions to Other Functions
	\end{enumerate}


	\section*{ Chapter 9: File I/O }

	\begin{enumerate}
		\item Creating a Data File
		\item Opening a Data File
		\item Reading from a Data File
		\item Writing to a Data File
		\item Closing a Data File
	\end{enumerate}


	\newpage

	\section*{ Chapter 10: Miscellaneous Topics }

	\begin{enumerate}
		\item Structure
		\item GUI Programming in C
		\item Introduction to GUI Programming with Qt
		\item Database Programming in C
		\item KISS Principle
		\item Code Debugging Techniques
		\item Common Error Messages
		\item Limitations of C Programming
		\item How to be a Better Programmer
		\item Problem Solving
		\item Online Judge
		\item Flowchart
		\item Exciting Technologies of the future: AI, ML, Blockchain, IoT
		\item What’s Next: Data Structures, Algorithms, OOP
	\end{enumerate}


	\section*{ Exams }

	\begin{enumerate}
		\item From Chapter-1 to Chapter-3
		\item From Chapter-4 to Chapter-6
		\item From Chapter-7 to Chapter-10
		\item General Problem Solving
	\end{enumerate}


	\em Note

	\begin{itemize}
		\item Exams will have both written and practical part.
		\item Written part may have MCQ, true / false, fill in the blanks, matching and short questions.
		\item Practical part will consists of problem solving.
		\item Final Exam will have only practical part.
	\end{itemize}
	
	\em \large Download the latest version from \url{https://github.com/Shakil-Shahadat/C}

\end{document}
